---
title: "Altruistic Behavior in Animal Populations"
output:
  html_document:
    keep_md: true
---

```{r include = FALSE}
library(simaltruism)
```

<br><br>
`simaltruist` provides a convenient interfacing for running simulations to explore the spread of gnes for altruism in an animal popluation.

## Scenario

Coming soon!

## Installation

Install the package from Git Hub:

```{r eval = FALSE}
devtools::install_github("homerhanumat/simlatruist")
```

Then attach the package:

```{r eval = FALSE}
library(simaltruist)
```

## Basic Usage

Here is a simple example:

```{r cache = TRUE, out.width = "90%", fig.align = "center", fig.cap = "A graph for free!"}
pop <- simulate(sim_gens = 400,
                warner_death_prob = 0.8)
```

Here's the data stored in `pop`:

```{r echo = FALSE}
DT::datatable(pop)
```

## Writing and Using Custom Functions

Coming soon!





##  Settings

`bpexploder` provides modest options for customization, as illustrated in the following example:

```{r}
bpexploder(data = chickwts,
           settings = list(
             yVar = "weight",
             # default NULL would make make one plot for yVar
             groupVar = "feed",
             levels = levels(with(chickwts,
                                  reorder(feed, weight, median))),
             # you could adjust the group labels ...
             levelLabels = NULL,
             # ... and the colors for each group:
             levelColors = RColorBrewer::brewer.pal(6, "Set3"),
             yAxisLabel = "6-week weight (grams)",
             xAxisLabel = "type of feed",
             tipText = list(
               # as many os you like of:
               # variableName = "desired tool-tip label"
               # leave tipText at NULL for no tips
               weight = "weight"),
             # set width relative to grandarent element of svg image:
             relativeWidth = 0.75,
             # default alignment within containing div is "center"
             # "left" and "right" are other possible values"
             align = "center",
             # aspect = width/height, defaults to 1.25
             aspect = 1.5)
           )
```

Here is another:

```{r}
survey <- tigerstats::m111survey
bpexploder(data = survey,
           settings = list(
             yVar = "fastest",
             groupVar = "seat",
             levelLabels = c("front", "middle", "back"),
             yAxisLabel = "fastest speed (mph)",
             xAxisLabel = "seating preference",
             tipText = list(
               sex = "sex",
               height = "height",
               fastest = "speed"),
             relativeWidth = 0.75)
           )
```


## Sizing

By default the box-plot chart sizes itself so that its width is the the setting `relativeWidth` (default-value 1) multiplied by the offset-width of its grandparent node in the HTML DOM.  For some layouts this might give you the type of control you want.  In that case you may direct `epexploder()` to make the width of the chart track the offset-width of an existing DOM element.  For example, if paragraphs in your document have the desired width, then create an empty paragraph in your markdown like this:

```
<p id="reference"></p>
```

To set the widget-width to a specific fraction of the element that contains the paragraph, you could again use the `relativeWidth` setting, or you might try something like: 

```
<p id="reference" style="width: 70%"></p>
```

<p id="reference" style="width: 70%"></p>

in either case, call `bpexploder()` with the `referenceId` setting:

```{r eval}
bpexploder(data = iris,
           settings = list(
             groupVar = "Species",
             levels = levels(iris$Species),
             yVar = "Petal.Length",
             tipText = list(
               Petal.Length = "Petal Length"
             ),
             # using <p id="reference" style="width: 70%"></p>
             referenceId = "reference")
           )
```

## Known Issues and Limitations

* Using the Leonids theme from the `prettydoc` R Markdown package, tool-tips are not visible in Firefox or Safari.  (They do show in Chrome.)
* When `htmlwidgets::createWidget()` creates a widget it gives the widget a random Id number.  For some reason this can result in spurious warnings concerning the hidden variable `.Random.Seed`.  To work around this, set a seed in the `setup` chunk of your R Markdown document, e.g.:

    ```{r eval = FALSE}
    library(bpexploder)
    set.seed(5437)  # one way to avoid .Random.Seed warning from widgetId creation
    ```


## Credits

The JavaScript library is based on Mathieu Caule's [D3 Exploding Boxplots](https://mcaule.github.io/d3_exploding_boxplot/), which I have modified slightly and updated for D3 Version 4. The tool-tips were created by [Justin Palmer](https://github.com/Caged), updated to D3v4 by [Dave Gotz](https://github.com/VACLab/d3-tip) and tweaked slightly by myself.
